---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval= FALSE, # Uncomment to run code
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# geniscrape

<!-- badges: start -->
[![R-CMD-check](https://github.com/basm92/geniscrape/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/basm92/geniscrape/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of geniscrape is to scrape genealogies and lineages from Geni.com in an efficient an easy way. 

## Installation

You can install the development version of geniscrape like so:

``` r
library(devtools)
install_github("basm92/geniscrape")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(geniscrape)
compute_family_df("https://www.geni.com/people/Lucas-Brouwer/6000000037332972722")
```

There are also two pre-loaded datasets by Moes (2012) included: 

```{r cars}
lijst_elite_moes

lijst_hoogst_aangeslagenen
```

## To do:

- Write a script contacting the API from openarch.nl
- Make links between different types of documents on wiewaswie.nl
  - E.g. go from marriage records to births: easy if there is a link, difficult if there is not
  - Implement `find_marriage_from_birth_wiewaswie` and `find_children_from_marriage_wiewaswie`
- Implement a name searching function on wiewaswie.nl based on some "blocking variables"
  - Same thing for other websites
- Create a function that, given a name, looks for candidates at all three (four) websites genealogieonline.nl, openarch.nl, geni.com and wiewaswie.nl
  - Work with complex interactions due to e.g. aristocrat names
- Implement a geni URL function to start from a list of geni.com URLS and retrieve a data.frame
- Implement a general method for fuzzy (uncertain) matching on wiewaswie based on empirics, e.g. age difference and (distance to) birthplace
  - Gather train data from prelabelled matches
- Implement a general method to match a geni profile to wiewaswie data (geboorten, overlijden, huwelijksactes)

- Maurits:
  - Install and have a look at `rvest`
  - Make sure `read_html_live()` works and you have the `chromote` package
  - Set up a Github account for collaboration
  - Important resources to browse through: [Github](https://floswald.github.io/ScPoProgramming/05-git.html#/title-slide) and [R Package Development](https://floswald.github.io/ScPoProgramming/05-git.html#/title-slide)
  
- Research oriented: 
  - Find a professional index on the basis of mariage records
  - Find fertility measures
  - Classify names to a religion on the basis of empirics
  - Study politicians' family links across $n$ generations
  
  

